%------------------------------------
% Dario Taraborelli
% Typesetting your academic CV in LaTeX
%
% URL: http://nitens.org/taraborelli/cvtex
% DISCLAIMER: This template is provided for free and without any guarantee 
% that it will correctly compile on your system if you have a non-standard  
% configuration.
% Some rights reserved: http://creativecommons.org/licenses/by-sa/3.0/
%------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[10pt, a4paper]{article}
\usepackage{fontspec} 
\usepackage{bbm, dsfont}

\usepackage{arev}



% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=6.0in, textheight=9.4in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{xunicode}
\usepackage{xltxtra}
\defaultfontfeatures{Mapping=tex-text}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}, Variant=01]{Linux Libertine O}
%\setmonofont[Scale=0.8]{Monaco}
%%% modified by Karol Kozioł for ShareLaTeX use
\setmainfont[
  Ligatures={Common}, Numbers={OldStyle}, Variant=01,
  BoldFont=LinLibertine_RB.otf,
  ItalicFont=LinLibertine_RI.otf,
  BoldItalicFont=LinLibertine_RBI.otf
]{LinLibertine_R.otf}
\setmonofont[Scale=0.8]{DejaVuSansMono.ttf}

% ---- CUSTOM COMMANDS
\chardef\&="E050
\newcommand{\html}[1]{\href{#1}{\scriptsize\textsc{[html]}}}
\newcommand{\pdf}[1]{\href{#1}{\scriptsize\textsc{[pdf]}}}
\newcommand{\doi}[1]{\href{#1}{\scriptsize\textsc{[doi]}}}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\amper{}}{\chardef\amper="E0BD }
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{20pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage[normalem]{ulem} 
\sectionfont{\mdseries\upshape\Large}
\subsectionfont{\mdseries\scshape\normalsize} 
\subsubsectionfont{\mdseries\upshape\large} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[%dvipdfm, 
bookmarks, colorlinks, breaklinks, 
% ---- FILL IN HERE THE TITLE AND AUTHOR
	pdftitle={Burak Ekici - vita},
	pdfauthor={My name},
	pdfproducer={http://ljk.imag.fr/membres/Burak.Ekici/}
]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue} 

% DOCUMENT
\begin{document}
{\LARGE Burak Ekici, Ph.D.}\\[0.25cm]
Muğla Sıtkı Koçman University, Department of Computer Engineering\\
%mail: Ziya Gökalp Caddesi No:48 06420, Kolej Çankaya, Ankara\\
%Bureau:  AK-2B02\\
%Phone: \texttt{+33 (0) 476 514 561}\\

\begin{tabular}{lll}
e-mail & : & \href{mailto:burakekici@muu.edu.tr}{burakekici@mu.edu.tr}\\
\textsc{url} & : & \href{http://ekiciburak.github.io/}{http://ekiciburak.github.io/}\\
%Born:  August 25, 1986---Turkey\\
Languages & : & Turkish (native), English (operational), French (inter.), Italian (inter.), German (notions)
\end{tabular}



\section*{Education \& Employment}

\years{\small2022-now} Assistant Professor at \textit{Department of Computer Engineering, Muğla Sıtkı Koçman University}, Muğla, Turkey.\\

\years{\small2021-2022} Assistant Professor at \textit{Department of Computer Engineering, TED University}, Ankara, Turkey.\\

\years{\small2019-2020} Assistant Professor at \textit{Department of Computer Engineering, İstanbul Kültür University}, İstanbul, Turkey.\\


\years{\small2018-2019} Post-Doctoral Research Fellow at \textit{Department of Computer Science, University of Innsbruck}, Innsbruck, Austria.\\
\emph{Project}: \textbf{CoqHammer.}\\
\emph{Advisor}: Cezary Kaliszyk.\\
\emph{With}: \L ukasz Czajka.\\

%\years{\small02.2017-12.2017} Civil Service in İzmir and Kilis, Turkey.\\

\years{\small2016-2017} Post-Doctoral Research Fellow at \textit{Department of Computer Science, The University of Iowa}, Iowa City-IA, USA.\\
\emph{Project}: \textbf{Integrating CVC4 into SMTCoq.}\\
\emph{Advisor}: Cesare Tinelli.\\
\emph{With}: Chantal Keller and Alain Mebsout.\\

\years{\small01.2013-12.2015} PhD Student at \textit{Department of Informatics, University Joseph Fourier}, Grenoble-France.\\
\emph{Thesis}: \textbf{Certification of programs with computational effects.}
 [\href{https://tel.archives-ouvertes.fr/tel-01250842v1/document}{manuscript}]
 [\href{http://ljk.imag.fr/membres/Burak.Ekici/PHDTHESIS/ekici_defense_slides.pdf}{slides}]
 \\
\emph{Advisors}: Jean-Guillaume Dumas, Dominique Duval, Damien Pous.\\

\years{\normalsize2009-2012} MSc Student at \textit{Department of Computer Engineering, Yaşar University}, Izmir-Turkey.\\
\emph{Thesis}: \textbf{A parallelization approach to Haskell language through category theoretic implementations.}\\
\emph{Advisor}: Ahmet H. Koltuksuz.\\

\years{\normalsize2010-2011} Trainee Researcher at \textit{European Commission Joint Research Centre},  Ispra(VA)-Italy.\\
\emph{Project}: \textbf{Linearity detection of the growth effect on children fingertips.}\\
\emph{Advisor}: Günter-Egon Schumacher.\\

\years{\normalsize2004-2009} BSc Student at \textit{Department of Computer Engineering, Izmir Institute of Technology}, Izmir-Turkey.\\
\emph{Thesis}: \textbf{Parallelization of mathematical functions of a cryptographic and multiprecision library, Crympix.}\\
\emph{Advisor}: Ahmet H. Koltuksuz.\\
\emph{With}: Görkem Kılınç and Çağatay Yücel.

\section*{Research Interests}
Computational effects, categorical logic, type theory, Coq, functional programming, Haskell, OCaml, SMT, hammer systems.

%\section*{Research Experience}
%\subsection*{Current Research}
%\years{\normalsize2011-2012} Undergraduate researcher $@$ Yaşar University, Izmir-Turkey.\\
%\years{\normalsize2010-2011} Trainee researcher $@$ European Commission Joint Research Centre, Ispra(VA)-Italy.\\
%\years{\normalsize2009-2010} Undergraduate researcher $@$ Yaşar University, Izmir-Turkey.\\
%\years{\normalsize2007-2009} Undergraduate researcher $@$ IS$^3$ Lab., Izmir-Turkey.


\section*{Publications \& Abstracts}
\subsection*{Journals}
%\years{\normalsize2017}
%Alain Mebsout, \emph{Burak Ekici}, Cesare Tinelli,
%Chantal Keller, Guy Katz, Andrew Reynolds and Clark Barrett. 
%\lq\lq{\href{http://ekiciburak.github.io/}{Automated Certified Proofs for Bit Vectors and Arrays in Coq.}}''
%(\emph{Submitted.})
%\\[0.25cm]

% \years{\normalsize2020}
%\emph{Burak Ekici}.
%\lq{}\lq{}Eilenberg-Moore Constructions in Coq.\rq{}\rq{} (Submitted to Journal of
%Formalized Reasoning)
% \\[0.25cm]
 \years{\normalsize2023}
\emph{Burak Ekici}.
{\href{https://www.mdpi.com/2075-1680/12/1/43/pdf}{A Sound Definitional Interpreter for a Simply Typed Functional Language}}, Axioms.
 \\[0.20cm]
 \years{\normalsize2022}
\emph{Burak Ekici}.
{\href{https://journals.tubitak.gov.tr/cgi/viewcontent.cgi?article=3178&context=math}{Formal categorical reasoning}}, Turkish Journal of Mathematics.
 \\[0.20cm]
 \years{\normalsize2020}
\emph{Burak Ekici}, Cezary Kaliszyk.
{\href{https://link.springer.com/content/pdf/10.1007%2Fs11786-020-00450-8.pdf}{Mac Lane’s Comparison Theorem for the Kleisli
Construction Formalized in Coq}}, Mathematics in Computer Science.
 \\[0.20cm]
\years{\normalsize2018}
\emph{Burak Ekici}.
\href{https://dmtcs.episciences.org/4927}{IMP with exceptions over decorated logic}, Discrete Mathematics and Theoretical Computer Science.
\subsection*{Conferences}
%\years{\normalsize2019}
%\L ukasz Czajka, \emph{Burak Ekici}, Ping Hou, and Cezary Kaliszyk.
%\lq\lq{\href{ekiciburak.io}{Boolean Reflection for Hammering Coq.}}''
%Submitted.
%\\[0.25cm]
\years{\normalsize2019}
\emph{Burak Ekici}, Arjun Viswanathan, Yoni Zohar, Clark Barrett, and Cesare
Tinelli.
{\href{http://pxtp.gforge.inria.fr/2019/papers/PxTP_2019_paper_5.pdf}{Verifying Bit-vector Invertibility Conditions in Coq (Extended Abstract)}}, 
Sixth Workshop on Proof eXchange for Theorem Proving (PxTP). Natal, Brazil, August 2019.
 \\[0.20cm]
\years{\normalsize2018}
\L ukasz Czajka, \emph{Burak Ekici}, Cezary Kaliszyk.
{\href{https://www.mimuw.edu.pl/~lukaszcz/cicm2018.pdf}{Concrete Semantics with Coq and CoqHammer}}, 
Proc. 11th Int. Conf. on Intelligent Computer Mathematics (CICM). Hagenberg, Austria, August 2018.
 \\[0.20cm]
\years{\normalsize2018}
\emph{Burak Ekici}.
{\href{https://www.cicm-conference.org/2018/infproc/paper11.pdf}{Towards Mac Lane's Comparison Theorem for the (co)Kleisli Construction in Coq}},
Proc. of the 3rd Formal Mathematics for Mathematicians (FMM), co-located with the 11th CICM. Hagenberg, Austria, August 2018.
 \\[0.20cm]
\years{\normalsize2017}
\emph{Burak Ekici}, Alain Mebsout, Cesare Tinelli,
Chantal Keller, Guy Katz, Andrew Reynolds and Clark Barrett. 
{\href{http://homepage.divms.uiowa.edu/~tinelli/papers/EkiEtAl-CAV-17.pdf}{SMTCoq: A plug-in for integrating SMT solvers into Coq}}, 
Proc. 29th Int. Conf. on Computer Aided Verification (CAV). Heidelberg, Germany, July 2017.
 \\[0.20cm]
\years{\normalsize2016}
\emph{Burak Ekici}, Guy Katz, Chantal Keller, Alain Mebsout, Andrew Reynolds and Cesare Tinelli.
{\href{http://eptcs.web.cse.unsw.edu.au/paper.cgi?HaTT2016.5}{Extending SMTCoq, a Certified Checker for SMT (Extended Abstract)}}, 
\emph{HaTT 2016: 1st International Workshop on Hammers for Type Theories, Coimbra, Portugal, July 2016.}
 \\[0.20cm]
\years{\normalsize2015}
Jean-Guillaume Dumas, Dominique Duval, \emph{Burak Ekici}, Damien Pous and Jean-Claude Reynaud. 
\href{https://hal.archives-ouvertes.fr/hal-01121924}{Hilbert-Post completeness for the state and the exception effects}, 
\emph{MACIS 2015: Sixth International Conference on Mathematical Aspects of Computer and Information Sciences, Berlin,
Germany, 11–13 November 2015.}
 \\[0.20cm]
%\years{\normalsize2015}\emph{Burak Ekici}. \lq\lq{}\href{https://hal.archives-ouvertes.fr/hal-01132831}{IMP with exceptions over decorated logic.}\rq\rq{} \textit{(presented at Trends in Functional Programming (TIFP 2015)).}\\[0.25cm]
\years{\normalsize2014}Jean-Guillaume Dumas, Dominique Duval, \emph{Burak Ekici} and Jean-Cluaude Reynaud. \href{https://hal.archives-ouvertes.fr/hal-00867237}{Certified proofs in programs involving exceptions}, \textit{CICM 2014 : Eigth Conference on Intelligent Computer Mathematics, Coimbra, Portugal, 7--11 July 2014,
CEUR Workshop Proceedings, no 1186, paper 20. }\\[0.25cm]
\years{\normalsize2014}Jean-Guillaume Dumas, Dominique Duval, \emph{Burak Ekici} and Damien Pous.
{\href{https://hal.archives-ouvertes.fr/hal-00869230}{Formal verification in Coq of program properties involving the global state effect}}, \textit{JFLA 2014 : Journées Francophones des Langages Applicatifs, Fréjus, France, 8--11 January 2014. }
 \\[0.20cm]
\years{\normalsize2010} \emph{Burak Ekici}, Çağatay Yücel, Görkem Kılınç, Ahmet H. Koltuksuz,
\href{http://ekiciburak.github.io/}{Implementations of Category Theory in Computer Science}, \emph{9th National Mathematics Symposium, Karadeniz Technical University, October 2010.}
 \\[0.20cm]
\years{\normalsize2010} K. Kratchanov, E. Golemanova, T. Golemanov, T. Ercan, \emph{B. Ekici}.
\href{http://arxiv.org/abs/1412.4184}{Implementation of Search Strategies in Control Network Programming}, \emph{Procedural and Non-Procedural In: Proc. Intl. Symposium in Innovations in Intelligent Systems
and Applications (INISTA 2010), June 2010, Kayseri, Turkey, 386-390.}
%\subsection*{Research Reports}
%\years{\normalsize2015}
%\emph{Burak Ekici}.
%``\href{https://hal.archives-ouvertes.fr/hal-01132831}{IMP with exceptions over decorated logic.}''
%\emph{Pre-proceedings of Trends in
%Functional Programming (TFP 2015). Rejected from the post-proceedings of TFP 2015 for basic improvements.}
\subsection*{Abstracts}
\years{\normalsize2022} \emph{Burak Ekici.}
\href{https://www.researchgate.net/profile/Rashid-Abu-Dawwas/publication/359082788_On_Graded_1-Absorbing_Primary_Ideals/links/6227168c97401151d206310f/On-Graded-1-Absorbing-Primary-Ideals.pdf#page=52}{Formal Categorical Reasoning}, \textit{Studies on Scientific Developments in Geometry, Algebra, and Applied
Mathematics (Online Event), 1-3 February 2022.}
 \\[0.20cm]
\years{\normalsize2014}Jean-Guillaume Dumas, Dominique Duval, \emph{Burak Ekici} and Damien Pous.
\href{http://arxiv.org/abs/1411.7140}{Program certification with computational effects}, \textit{Journées Nationales de Calcul Formel (JNCF) 2014, Marseille, France Novermber 2014.}
\\[0.25cm]
\years{\normalsize2014} \emph{Burak Ekici.}
\href{http://arxiv.org/abs/1411.7139}{Certification of programs with computational effects},
\textit{Doctoral session. CICM 2014 : Eigth Conference on Intelligent Computer Mathematics, Coimbra, Portugal, 7--11 July 2014.}

%\subsection*{Preprints}
% \years{\normalsize2020}
%\emph{Burak Ekici}.
%\lq{}\lq{}Eilenberg-Moore Constructions in Coq.\rq{}\rq{} (Submitted to Journal of
%Formalized Reasoning)
% \\[0.25cm]

\section*{Teaching}
\years{\normalsize2020--2023}Main Course: Formal Languages and Abstract Machines  
\\[0.25cm]
\years{\normalsize2022-2023}Main Course: Functional Programming (Haskell)  
\\[0.25cm]
\years{\normalsize2021-2022}Main Course: Category Theory in Computer Science 
\\[0.25cm]
\years{\normalsize2021-2022}Main Course: Fundamentals of Programming I 
\\[0.25cm]
\years{\normalsize2019-2020}Main Course: Digital Design 
\\[0.25cm]
\years{\normalsize2019-2020}Main Course: Microprocessors 
\\[0.25cm]
\years{\normalsize2019-2020}Main Course: Programming Languages
\\[0.25cm]
\years{\normalsize2018-2019}Proseminar: Discrete Mathematics

 


\section*{Recent Talks}
\subsection*{Invited}
\years{\normalsize 07.06.2019}\href{http://cj-xu.github.io/tim19/index.html}{Univalent Typoids in Coq.}  Ludwig-Maximilians-Universität, Munich-Germany.\\[0.25cm]
\years{\normalsize 27.12.2018}{Decorated semantics for an imperative language with exceptions.} Özyeğin University, İstanbul-Turkey.\\[0.25cm]
\years{\normalsize10.11.2015} \href{http://www.fmf.uni-lj.si/si/obvestila/35243/}{Relative Hilbert-Post completeness for exceptions.} Foundations Seminar, Ljubljana-Slovenia.
\subsection*{Others}
\years{\normalsize 01.02.2022}{Formal Categorical Reasoning.}
 \href{https://etkinlik.ulakbim.gov.tr/event/12/}{Studies on Scientific Developments in Geometry, Algebra, and Applied
Mathematics.} (online event)\\[0.25cm]
\years{\normalsize 27.03.2019}{Univalent Type Theory.} Master Seminar, University of Innsbruck-Austria.\\[0.25cm]
%\years{\normalsize 27.12.2018}{Decorated semantics for an imperative language with exceptions.} Master Seminar, University of Innsbruck-Austria.\\[0.25cm]
\years{\normalsize15.08.2018} \href{https://cicm-conference.org/2018/slides/T16.pdf}{Concrete Semantics with Coq and
CoqHammer.} CICM'18 Hagenberg-Austria.\\[0.25cm]
\years{\normalsize13.08.2018} \href{https://cicm-conference.org/2018/slides/FMM5.pdf}{Towards Mac Lane's Comparison Theorem for the (co)Kleisli construction in Coq.} FMM'18 Hagenberg-Austria.\\[0.25cm]
\years{\normalsize31.05.2018} \href{http://cl-informatik.uibk.ac.at/teaching/ss18/ms2/slides/BE.pdf}{SMTCoq, a plug-in for the trustworthy integration of SAT/SMT solvers into Coq.} Master Seminar, University of Innsbruck-Austria.\\[0.25cm]
\years{\normalsize03.06.2015} \href{ftp://ftp-sop.inria.fr/indes/TFP15/TFP2015_talk_6.pdf}{ IMP with exceptions over decorated logic.} TFP'15, Sophia-Antipolis-France.\\[0.25cm]
%\years{\normalsize20.11.2014} \href{http://www-ljk.imag.fr/Seminars/1415889734530/Ekici_casys-meff.pdf}{ Certification of programs with computational effects.} CASYS-MEFF Seminars, Grenoble-France.\\[0.25cm]
\years{\normalsize05.11.2014} \href{http://www.lifl.fr/jncf2014/files/slides/ekici.pdf}{Program certification with computational effects.} JNCF'14, Marseille-France.\\[0.25cm]
\years{\normalsize11.07.2014} \href{http://ljk.imag.fr/membres/Burak.Ekici/CICM14/BurakEkici_presentation.pdf}{ Certification of programs with computational effects.} CICM'14, Coimbra-Portugal.\\[0.25cm]
%\years{\normalsize18.02.2014} \href{http://ljk.imag.fr/membres/Burak.Ekici/BurakEkici_IMP_EXC.pdf}{\{IMP + Exc\} over Decorated Logic.} LJK, Grenoble-France.\\[0.25cm]
\years{\normalsize09.01.2014} \href{http://jfla.inria.fr/2014/ekici.pdf}{ Formal verification in Coq of program properties involving the global state effect.} JFLA'2014, Fréjus - France.\\[0.25cm]
\years{\normalsize05.12.2013} \href{http://ljk.imag.fr/membres/Burak.Ekici/BurakEkici_LJK-Seminar.pdf}{ Formal verification in Coq of program properties involving the global state effect.}
Séminaires LJK-Modèles et Algorithmes Déterministes: BIPOP-CASYS, Grenoble-France.
%\years{\normalsize11.10.2013} \href{http://ljk.imag.fr/membres/Burak.Ekici/BurakEkici_ExpLJK.pdf}{Proofs About Programs Involving Computational Effects.} Exposé au LJK, Grenoble-France.\\[0.25cm]
%\years{\normalsize23.05.2013} \href{http://ejcp2013.inria.fr/files/student_presentations/Burak.Ekici.pdf}{Certification of Programs with Computational Effects.} EJCP 2013, Dinard-France.

\section*{Events Attended}
\subsection*{Invited}
\years{\small 07.06.2019} \href{http://cj-xu.github.io/tim19/index.html}{Types in Munich} (invited by Dr. Iosif Petrakis), Ludwig-Maximilians-Universität, Munich-Germany.\\[0.25cm]
\years{\small09-13.11.15} University of Ljubljana (invited by Dr. Andrej Bauer), Ljubljana, Slovenia.
\subsection*{Others}
\years{\small13-17.08.18} Conferences on Intelligent Computer Mathematics (CICM'18), Hagenberg-Austria.\\[0.25cm]
\years{\small25-30.03.18} 3rd Conference on Artificial Intelligence and Theorem Proving (AITP'18), Aussois-France.\\[0.25cm]
\years{\small03-05.06.15} The Sixteenth Symposium on Trends in Functional Programming (TIFP'15), INRIA, Sophia-Antipolis-France.\\[0.25cm]
\years{\small26-29.05.15}  Colloque Inter'Actions en Mathématiques 2015 (member of the
organization committee), 
Institut Fourier, Grenoble-France.\\[0.25cm]
\years{\small03-07.11.14} Journées Nationales de Calcul Formel (JNCF'14), CIRM, Marseille-France.\\[0.25cm]
\years{\small07-11.07.14} Conferences on Intelligent Computer Mathematics (CICM'14), Coimbra-Portugal.\\[0.25cm]
\years{\small07-18.04.14} PhD school on semantics of proofs and certified mathematics by Institut Henri Poincaré, CIRM, Marseille-France. \\[0.25cm]
\years{\small07-11.01.14} JFLA: Journées Francophones des Langages Applicatifs, La-villa-clythia, Fréjus-France. \\[0.25cm]
\years{\small23-31.05.13} École Jeunes Chercheurs en Programmation, Inria, Rennes-France.
%\years{\normalsize17-29.04.12} IWOSI: The Information Warfare, Cyber Warfare and Open Sources Intelligence
%(member of the organization committee), Izmir-Turkey. \\[0.25cm]
%\years{\normalsize01-02.09.09} Workshop on The Security of Information and Communication Technologies: A
%Turkey \& EC-JRC Joint Effort, Izmir-Turkey.\\[0.25cm]
%\years{\normalsize25-26.09.09}Workshop on Multi-Core Architectures \& Parallel Programming with Intel Software
%Tools (member of the organization committee), Izmir-Turkey. 
\section*{Code}
Please see my \href{https://github.com/ekiciburak}{github repository.}
\section*{Miscellaneous}
Programming: C/C++, Java, Haskell, OCaml, Coq, Lean. \\
Libraries: CRYMPIX, OpenMP, WHY3, SMTCoq, CoqHammer.
\section*{Referees}
\href{http://ljk.imag.fr/membres/Jean-Guillaume.Dumas/}{Jean-Guillaume Dumas} \hfill \href{http://ljk.imag.fr/membres/Dominique.Duval/}{Dominique Duval}\\
LJK, University Grenoble Alpes \hfill LJK, University Grenoble Alpes\\
%Phone: +33 (0) 457 421 732 \hfill Phone: +33 (0) 457 421 734 \\
email: \href{mailto:jean-guillaume.dumas@univ-grenoble-alpes.fr}{jean-guillaume.dumas@univ-grenoble-alpes.fr} \hfill email: \href{mailto:dominique.duval@univ-grenoble-alpes.fr}{dominique.duval@univ-grenoble-alpes.fr}\\

\href{http://homepage.cs.uiowa.edu/~tinelli/index.html}{Cesare Tinelli}\hfill \href{http://cl-informatik.uibk.ac.at/users/cek/}{Cezary Kaliszyk}\\
Department of Computer Science, \hfill Computational Logic Group,\\
The University of Iowa \hfill University of Innsbruck\\
%Phone: +1-319-335-0735\\
email: \href{mailto:cesare-tinelli@uiowa.edu}{cesare-tinelli@uiowa.edu} \hfill email: \href{mailto:cezary.kaliszyk@uibk.ac.at}{cezary.kaliszyk@uibk.ac.at}\\


\href{https://bm.iku.edu.tr/tr/bilgisayar-muhendisligi-bolumu-akademik-kadro}{Murat Taylı}\hfill\\
Department of Computer Engineering, \hfill \\
İstanbul Kültür University \hfill \\
%Phone: +1-319-335-0735\\
email: \href{mailto: m.tayli@iku.edu.tr}{m.tayli@iku.edu.tr} \hfill 
\begin{center}
{\scriptsize  Last updated:\today\- •\- 
% ---- PLEASE LEAVE THIS BACKLINK FOR ATTRIBUTION AS PER CC-LICENSE
Typeset in \href{http://en.wikipedia.org/wiki/XeTeX}{
%\fontspec{Times New Roman}
\XeTeX}}
% ---- FILL IN THE FULL URL TO YOUR CV HERE
%\href{http://ljk.imag.fr/membres/Burak.Ekici/}{http://ljk.imag.fr/membres/Burak.Ekici/}}
\end{center}

\end{document}